%-------------------------
% Northwestern Style Resume - Modern & Clean
% Author: Xuanyou (Zed) Liu
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{geometry}

% -------------------- FONT OPTIONS --------------------
% sans-serif font for a more modern, clean look
\usepackage[sfdefault]{roboto}  % Roboto font
\usepackage[T1]{fontenc}

% -------------------- PAGE LAYOUT --------------------
\geometry{left=0.5in, top=0.5in, right=0.5in, bottom=0.5in}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.5pt} % Fix fancyhdr warning

% Adjust margins
\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% -------------------- COLORS --------------------
% Northwestern Purple
\definecolor{NUPurple}{HTML}{4E2A84}
% Darker text for better readability
\definecolor{DarkText}{HTML}{1a1a1a}
\definecolor{GrayText}{HTML}{555555}

% -------------------- SECTION FORMATTING --------------------
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\Large\color{NUPurple}\bfseries
}{}{0em}{}[\color{NUPurple}\titlerule \vspace{-4pt}]

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small \color{GrayText} #2} \\
      \textit{\small #3} & \textit{\small \color{GrayText} #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small \color{GrayText} #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% -------------------- HEADING --------------------
\begin{center}
    {\Huge \scshape \bfseries \color{NUPurple} Xuanyou (Zed) Liu} \\[6pt]
    \small 
    {\color{NUPurple}\faMapMarker*} Evanston, IL \quad 
    {\color{NUPurple}\faPhone} (+1) 267-809-0364 \quad
    {\color{NUPurple}\faEnvelope} \href{mailto:xuanyou@u.northwestern.edu}{xuanyou@u.northwestern.edu} \quad
    {\color{NUPurple}\faGlobe} \href{https://xuanyouliu.com}{xuanyouliu.com}
\end{center}
\vspace{4pt}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northwestern University}{Evanston, USA}
      {Ph.D. in Computer Science \textnormal{\textbar\ \textit{Advisor: Prof. Karan Ahuja}}}{Sep 2025 -- 2030 (expected)}
      \resumeItemListStart
        \resumeItem{\textbf{Research Focus:} Human Computer Interaction (HCI)}
        \resumeItem{\textbf{Honors:} TGS First-Year Fellowship}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Pennsylvania}{Philadelphia, USA}
      {M.S.E. in Robotics \textnormal{\textbar\ \textit{GPA: 4.00/4.00, Rank: 1/64}}}{Sep 2023 -- May 2025}
      \resumeItemListStart
         \resumeItem{\textbf{Honors:} GAPSA Professional Student Travel Award (2025)}
      \resumeItemListEnd

    \resumeSubheading
      {Xi'an Jiaotong University}{Xi'an, China}
      {B.E. in Industrial Design \textnormal{\textbar\ \textit{GPA: 3.86/4.30, Rank: 1/21}}}{Sep 2019 -- Jul 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Honors:} Outstanding Graduate, Outstanding Student Leader}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------- PUBLICATIONS --------------------
\section{Selected Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Seeing with the Hands: A Sensory Substitution That Supports Manual Interactions}}{CHI 2025}
      \resumeItemListStart
        \resumeItem{Shan-Yuan Teng*, Gene Kim*, \textbf{\color{NUPurple} Xuanyou Liu*}, Pedro Lopez (*equal contribution)}
        \resumeItem{Conference on Human Factors in Computing Systems (CHI) \href{https://doi.org/10.1145/3613904.3642063}{\color{NUPurple}\faExternalLink*}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{TacTex: A Textile Interface with Seamlessly-Integrated Electrodes}}{CHI 2024}
      \resumeItemListStart
        \resumeItem{Hongnan Lin, \textbf{\color{NUPurple} Xuanyou Liu}, Shengsheng Jiang, Qi Wang, Ye Tao, et al.}
        \resumeItem{Conference on Human Factors in Computing Systems (CHI) \href{https://doi.org/10.1145/3613904.3642063}{\color{NUPurple}\faExternalLink*}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------- PROJECTS --------------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Robust EIT for Hand Tracking with Contrastive Learning} $|$ \emph{Northwestern University}}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built a transformer-based contrastive learning model to enable continuous hand pose tracking across users and arm poses.}
        \resumeItem{Designed a compact PCB and implemented real-time firmware using RTOS for high-frequency bio-impedance sensing.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Compact Electrotactile Module for Wearable Haptics} $|$ \emph{UPenn Independent Study}}{Aug 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{Developed a miniaturized electrotactile stimulation module for high-fidelity haptic feedback in wearables.}
        \resumeItem{Designed custom PCB and firmware for real-time control and integration with VR environments.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Ins-Bucks Food 3D Printer} $|$ \emph{RCA-Imperial Design Competition}}{Jun 2021 -- Jul 2021}
      \resumeItemListStart
        \resumeItem{Designed an insect-based 3D food printing service ecosystem integrating hardware, UI, and service blueprints.}
        \resumeItem{Received \textbf{Most Innovative Award} for the novel application of sustainable protein in personalized nutrition.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Luxottica Tristar Optical Co., Ltd.}{Dongguan, China}
      {R\&D Intern, Component Factory}{Jul 2020 -- Sep 2020}
      \resumeItemListStart
        \resumeItem{Enhanced lost-wax casting processes by optimizing temperature parameters, reducing defect rate by 15\%.}
        \resumeItem{Refactored Ladder Logic code for the production line PLC, improving cycle time efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------- SKILLS & AWARDS --------------------
\section{Skills \& Leadership}
  \resumeSubHeadingListStart
    \item{
      \textbf{Leadership:} Teaching Assistant (Smart Devices), UNICEF Volunteer, Code Instructor (Fife-Penn) \\
      \vspace{3pt}
      \textbf{Skills:} HCI, Haptics, Robotics, PCB Design, CAD (SolidWorks), Python, C++, MATLAB, LaTeX
    }
  \resumeSubHeadingListEnd

\end{document}
